---
title: "Movie Memory Test"
subtitle: "BRSM Mid-Semester Project Report"
author: "Vibe Coders"

output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    number_sections: true
    df_print: kable
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  message   = FALSE,
  warning   = FALSE,
  fig.align = "center",
  fig.width  = 8,
  fig.height = 5
)
```

```{r packages, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(scales)
library(readxl)
library(tibble)
library(tidyr)
library(purrr)
```

```{r load-data, include=FALSE}
data_folder <- "BRSM data csv/BRSM data csv"
csv_files <- list.files(path = data_folder, pattern = "\\.csv$", full.names = TRUE)

read_participant <- function(f) {
  df <- tryCatch(
    read_csv(f, col_types = cols(.default = col_character()), show_col_types = FALSE),
    error = function(e) NULL
  )
  if (is.null(df)) return(NULL)
  # case-insensitive match handles both "sub21_NB" (2-digit) and "sub100_AB" (3-digit)
  # and capitalisation variants like "Sub41_AB"
  fname <- basename(f)
  df$participant_id <- str_to_lower(str_extract(fname, "(?i)^sub[0-9]+"))
  df$condition_raw  <- str_extract(fname, "(?i)(?<=sub[0-9]{2,3}_)[A-Z]+")
  df
}

raw_list <- map(csv_files, read_participant)
raw_df   <- bind_rows(raw_list)
```

## Encoding Time Exclusion

```{r encoding-time-exclusion, include=FALSE}
# Calculate encoding time for each participant
# Encoding time = time between end of instructions (instruction_2.stopped) 
# and start of recognition phase (recognition.started)

encoding_times <- raw_df %>%
  filter(!is.na(participant_id)) %>%
  group_by(participant_id) %>%
  summarise(
    instruction_stopped = suppressWarnings(as.numeric(first(na.omit(`instruction_2.stopped`)))),
    recognition_started = suppressWarnings(as.numeric(first(na.omit(`recognition.started`)))),
    .groups = "drop"
  ) %>%
  mutate(
    encoding_time_sec = recognition_started - instruction_stopped,
    encoding_time_min = encoding_time_sec / 60
  )

# Set threshold to 27.05 minutes (as per experimental protocol)
encoding_threshold_min <- 27.05

# Identify participants who exceeded the encoding time limit
encoding_excluded_ids <- encoding_times %>%
  filter(!is.na(encoding_time_min), encoding_time_min > encoding_threshold_min) %>%
  pull(participant_id)

n_encoding_excluded <- length(encoding_excluded_ids)
n_total_loaded <- n_distinct(raw_df$participant_id)
n_after_encoding <- n_total_loaded - n_encoding_excluded

cat("\n=== ENCODING TIME EXCLUSION ===", "\n")
cat("Total participants loaded:", n_total_loaded, "\n")
cat("Encoding time threshold:", encoding_threshold_min, "minutes\n")
cat("Participants excluded (encoding time >" , encoding_threshold_min, "min):", n_encoding_excluded, "\n")
if (n_encoding_excluded > 0) {
  cat("Excluded participant IDs:", paste(encoding_excluded_ids, collapse = ", "), "\n")
  encoding_times %>% 
    filter(participant_id %in% encoding_excluded_ids) %>%
    select(participant_id, encoding_time_min) %>%
    print()
}
cat("Participants retained:", n_after_encoding, "\n")
cat("\n")

# Apply encoding time exclusion
raw_df <- raw_df %>% filter(!participant_id %in% encoding_excluded_ids)
```

```{r encoding-exclusion-table}
tibble(
  Stage = c(
    "Initial N (files loaded into master dataframe)",
    paste0("Excluded - encoding time > ", encoding_threshold_min, " min"),
    "Final N for analysis"
  ),
  Count = c(
    n_total_loaded,
    n_encoding_excluded,
    n_after_encoding
  )
) %>% knitr::kable()
```

**Encoding Time Exclusion Rationale:** Participants who took longer than 27.05 minutes between the end of video-watching instructions and the start of the recognition phase were excluded. Excessive delays suggest interruptions, technical issues, or anomalous session behavior that could compromise data quality. This window captures the complete 40-video encoding phase plus transition time.

```{r encoding-excluded-details}
if (n_encoding_excluded > 0) {
  encoding_times %>%
    filter(participant_id %in% encoding_excluded_ids) %>%
    mutate(encoding_time_min = round(encoding_time_min, 1)) %>%
    select(`Participant` = participant_id, `Encoding Time (min)` = encoding_time_min) %>%
    knitr::kable(
      caption = "Participants excluded due to excessive encoding time"
    )
}
```

---

# Introduction

This report presents the analysis of a **movie memory test** (BRSM mid-semester project). The study investigates how the position of a video clip's ending relative to a natural event boundary affects later recognition memory for individual video frames.

The theoretical foundation is **Event Segmentation Theory (EST; Zacks et al., 2007)**. When a natural event boundary is encountered, the current event model is updated and the prior model is consolidated into long-term memory, enhancing recognition memory for boundary-adjacent frames.

Participants watched short video clips ending at a natural event boundary (**NB** condition) or cut abruptly before the boundary (**AB** condition). They then completed a recognition memory test identifying the correct target frame from two alternatives.

---

# Hypotheses and Variables

## Research Hypotheses

**H1 - Condition effect on recognition accuracy:**
NB participants will show significantly higher overall recognition accuracy than AB participants. Intact event boundaries strengthen memory encoding through event model updating.

**H2 - Boundary frame advantage:**
NB-BB accuracy will be higher than AB-BB accuracy. The memory benefit of natural boundaries is linked specifically to boundary-adjacent frames.

**H3 - Event-middle frame null effect:**
NB-EM and AB-EM accuracy will not differ significantly. If the boundary benefit is specific to boundary-adjacent frames, EM frames should be unaffected.

## Variables

| Role | Variable | Type | Description |
|------|----------|------|-------------|
| - | `participant_id` | Character | Unique participant identifier |
| - | `movie_id` | Integer (1-40) | Which of the 40 video clips the trial belongs to |
| **IV (between-subjects)** | `Condition` | Factor (NB/AB) | Natural Boundary vs Abrupt Boundary |
| **IV (within-subjects)** | `FrameType` | Factor (BB/EM) | Before-Boundary or Event-Middle probe frame |
| **Primary DV** | `Accuracy` | Numeric (0/1) | 1 if the target frame was correctly identified |
| **Secondary DV** | `RT` | Numeric (seconds) | Response time |
| **Secondary DV** | `Confidence` | Numeric | Self-rated confidence on the recognition decision |

## Statistical Analysis Plan

All inferential tests use independent-samples **Welch t-tests**. Four primary tests address experimental hypotheses (Bonferroni-adjusted alpha = 0.0125). Four demographic tests evaluate randomisation and moderators (alpha = 0.05).

### Multiple Comparison Correction

Because we conduct **4 primary hypothesis tests** on the same dataset, we apply **Bonferroni correction** to control the family-wise error rate. Without correction, the probability of making at least one Type I error would be ~18.6% instead of the desired 5%.

$$\alpha_{adjusted} = \frac{0.05}{4} = 0.0125$$

This means **p-values must be < 0.0125** (not 0.05) to be considered statistically significant for Tests 1-4.

---

# Data Cleaning and Preprocessing

## Trial Count Exclusion

```{r participant-exclusion, include=FALSE}
trial_counts <- raw_df %>%
  filter(!is.na(participant_id)) %>%
  group_by(participant_id) %>%
  summarise(n_rows = n(), .groups = "drop")

excluded_ids <- trial_counts %>% filter(n_rows < 20) %>% pull(participant_id)
n_excluded   <- length(excluded_ids)
n_total_after_encoding      <- n_distinct(raw_df$participant_id)
n_included   <- n_total_after_encoding - n_excluded

cat("\n=== TRIAL COUNT EXCLUSION ===", "\n")
cat("Participants after encoding time filter:", n_total_after_encoding, "\n")
cat("Participants excluded (< 20 valid trials):", n_excluded, "\n")
cat("Participants retained:", n_included, "\n")
cat("\n")
```

```{r filter-participants, include=FALSE}
clean_df <- raw_df %>% filter(!participant_id %in% excluded_ids)
```

Each participant contributed one CSV file. After encoding time exclusion, participants were further excluded if their file contained fewer than 20 recognisable data rows, which would indicate an incomplete or corrupted recognition phase session.

```{r exclusion-table}
tibble(
  `Processing Stage` = c(
    "Participant CSV files loaded",
    paste0("Excluded - encoding time > ", encoding_threshold_min, " min"),
    "After encoding time filter",
    "Excluded - fewer than 20 valid data rows",  
    "Final participant count for analysis"
  ),
  `Number of Participants` = c(
    n_total_loaded, 
    n_encoding_excluded,
    n_after_encoding,
    n_excluded, 
    n_included
  )
) %>% knitr::kable()
```

## Variable Derivation

```{r derive-variables}
trial_df <- clean_df %>%
  filter(!is.na(movie_id), !is.na(`resp.corr`)) %>%
  mutate(movie_id_num = suppressWarnings(as.integer(movie_id))) %>%
  filter(!is.na(movie_id_num), movie_id_num >= 1, movie_id_num <= 40) %>%
  mutate(
    Condition  = factor(str_to_upper(condition_raw), levels = c("NB", "AB")),
    FrameType  = factor(case_when(
      str_detect(target_img, "BB") ~ "BB",
      str_detect(target_img, "EM") ~ "EM",
      TRUE ~ NA_character_
    ), levels = c("BB", "EM")),
    Accuracy   = suppressWarnings(as.numeric(`resp.corr`)),
    RT         = suppressWarnings(as.numeric(str_trim(str_remove_all(`resp.rt`, "[\\[\\]\\s]")))),
    Confidence = suppressWarnings(as.numeric(`conf_radio.response`))
  ) %>%
  filter(!is.na(Accuracy), !is.na(Condition), !is.na(FrameType)) %>%
  select(participant_id, Condition, FrameType, movie_id = movie_id_num, Accuracy, RT, Confidence)

n_trials_before_rt <- nrow(trial_df)
rt_mean       <- mean(trial_df$RT, na.rm = TRUE)
rt_sd         <- sd(trial_df$RT,   na.rm = TRUE)
rt_cutoff     <- rt_mean + 3 * rt_sd
n_rt_outliers <- sum(!is.na(trial_df$RT) & trial_df$RT > rt_cutoff)
n_below_200ms <- sum(!is.na(trial_df$RT) & trial_df$RT < 0.2)

cat(sprintf("\n=== RT OUTLIER REMOVAL ===\n"))
cat(sprintf("Trials with RT < 200 ms (implausibly fast): %d\n", n_below_200ms))
cat(sprintf("RT mean = %.0f ms, SD = %.0f ms\n", rt_mean * 1000, rt_sd * 1000))
cat(sprintf("Mean + 3SD cutoff = %.0f ms\n", rt_cutoff * 1000))
cat(sprintf("Trials removed (RT > Mean+3SD): %d (%.1f%%)\n", n_rt_outliers, 100 * n_rt_outliers / n_trials_before_rt))

trial_df <- trial_df %>% filter(is.na(RT) | RT <= rt_cutoff)
cat("Final trial count after RT filter:", nrow(trial_df), "\n")
cat("Final participant count:", n_distinct(trial_df$participant_id), "\n\n")
```

### RT Outlier Removal Details

```{r rt-statistics-table}
tibble(
  Statistic = c(
    "Trials with RT < 200 ms (implausibly fast)",
    "RT mean",
    "RT SD", 
    "Mean + 3SD cutoff",
    "Trials removed (RT > Mean+3SD)",
    "Final trial count after RT filter",
    "Final participant count"
  ),
  Value = c(
    paste0(n_below_200ms),
    paste0(round(rt_mean * 1000), " ms"),
    paste0(round(rt_sd * 1000), " ms"),
    paste0(round(rt_cutoff * 1000), " ms"),
    paste0(n_rt_outliers, " (", round(100 * n_rt_outliers / n_trials_before_rt, 1), "%)"),
    nrow(trial_df),
    n_distinct(trial_df$participant_id)
  )
) %>% knitr::kable()
```

The table below tracks how many trials were removed at each cleaning step. Only rows with a valid `movie_id` (1–40), a recorded response, and a response time within three standard deviations of the mean were kept.

```{r trial-exclusion-table}
n_after_participant <- nrow(clean_df)
n_initial_trials <- n_trials_before_rt
n_na_removed <- n_after_participant - n_initial_trials

tibble(
  Stage = c(
    "Total rows in loaded data (after participant exclusion)",
    "Rows removed - NA in movie_id or resp.corr (non-trial rows)",
    "Remaining recognition trials (movie_id 1-40)",
    "Trials with RT < 200 ms (implausibly fast) - none found",
    paste0("Trials excluded - RT > Mean+3SD (> ", round(rt_cutoff * 1000), " ms)"),
    "Final trial count for analysis"
  ),
  Count = c(
    n_after_participant,
    n_na_removed,
    n_initial_trials,
    n_below_200ms,
    n_rt_outliers,
    nrow(trial_df)
  )
) %>% knitr::kable()
```

## Load Demographic Data

```{r load-demographics, include=FALSE}
demo_df <- read_excel("BRSM data csv/Demographic data.xlsx") %>%
  rename(raw_id = `Sub ID`) %>%
  mutate(
    raw_id        = str_trim(str_to_lower(raw_id)),
    Condition     = str_extract(raw_id, "(?i)(?<=sub[0-9]{2,3}_)[A-Za-z]+") %>% str_to_upper(),
    # Strip _nb / _ab suffix; lower-case to match CSV-derived IDs (e.g. "sub21", "sub100")
    participant_id = str_to_lower(str_extract(raw_id, "(?i)^sub[0-9]+")),
    Age            = suppressWarnings(as.numeric(Age))
  )

demo_complete <- demo_df %>% filter(!is.na(Age))
cat("Demographic register rows:", nrow(demo_df), "\n")
cat("Complete age records:", nrow(demo_complete), "\n")
cat("Sample demo IDs:", paste(head(demo_complete$participant_id, 3), collapse=", "), "\n")
```

## Participant Demographics

Of 185 register entries, **163 participants** had complete demographic records; **22** had no demographic information.

---

### Comprehensive Descriptive Statistics - Demographics

#### Age Statistics (Detailed)

```{r age-descriptives-detailed}
age_stats <- demo_complete %>%
  summarise(
    N                = n(),
    Mean             = mean(Age),
    Median           = median(Age),
    `Std Dev`        = sd(Age),
    Variance         = var(Age),
    `Std Error`      = sd(Age) / sqrt(n()),
    Minimum          = min(Age),
    Maximum          = max(Age),
    Range            = max(Age) - min(Age),
    Q1               = quantile(Age, 0.25),
    Q3               = quantile(Age, 0.75),
    IQR              = IQR(Age),
    `Coef of Var %`  = (sd(Age) / mean(Age)) * 100
  )

age_stats %>%
  pivot_longer(everything(), names_to = "Statistic", values_to = "Value") %>%
  mutate(Value = round(Value, 2)) %>%
  rename(`Age Statistic` = Statistic, `Value (years or count)` = Value)
```

**Interpretation:** The sample is predominantly young adults with mean age `r round(mean(demo_complete$Age), 1)` years (SD = `r round(sd(demo_complete$Age), 1)`). The distribution spans from `r min(demo_complete$Age)` to `r max(demo_complete$Age)` years, with 50% of participants between `r quantile(demo_complete$Age, 0.25)` and `r quantile(demo_complete$Age, 0.75)` years (IQR).

#### Age Distribution by Condition

```{r age-by-condition-detailed}
age_by_cond <- demo_complete %>%
  group_by(Condition) %>%
  summarise(
    N                    = n(),
    Mean                 = mean(Age),
    Median               = median(Age),
    `Std Dev`            = sd(Age),
    `Std Error`          = sd(Age) / sqrt(n()),
    Minimum              = min(Age),
    Maximum              = max(Age),
    Range                = max(Age) - min(Age),
    Q1                   = quantile(Age, 0.25),
    Q3                   = quantile(Age, 0.75),
    .groups = "drop"
  )

age_by_cond %>%
  mutate(across(where(is.numeric) & !N, ~round(.x, 2)))
```

**Key Finding:** Both conditions show remarkably similar age distributions, supporting successful randomization.

#### Gender Frequency Distribution

```{r gender-frequency-detailed}
gender_freq <- demo_complete %>%
  count(Gender, name = "Frequency") %>%
  mutate(
    Percentage       = round((Frequency / sum(Frequency)) * 100, 1),
    `Cumulative %`   = round(cumsum(Percentage), 1)
  ) %>%
  arrange(desc(Frequency))

gender_freq
```

**Summary:** The sample is `r round((sum(demo_complete$Gender == "Male") / nrow(demo_complete)) * 100, 1)`% male and `r round((sum(demo_complete$Gender == "Female") / nrow(demo_complete)) * 100, 1)`% female, reflecting a male-skewed convenience sample typical of certain university populations.

#### Gender by Condition Cross-Tabulation

```{r gender-condition-crosstab}
gender_cond_table <- table(demo_complete$Gender, demo_complete$Condition)

gender_cond_df <- as.data.frame.matrix(gender_cond_table) %>%
  rownames_to_column("Gender") %>%
  mutate(
    Total        = NB + AB,
    `% of Total` = round((Total / sum(Total)) * 100, 1),
    `% within NB` = round((NB / sum(NB)) * 100, 1),
    `% within AB` = round((AB / sum(AB)) * 100, 1)
  )

gender_cond_df
```

**Interpretation:** Gender distribution is balanced across conditions (Chi-squared test confirms no significant difference, see Test D2).

#### Handedness Frequency Distribution

```{r handedness-frequency-detailed}
handedness_freq <- demo_complete %>%
  count(Handedness, name = "Frequency") %>%
  mutate(
    Percentage       = round((Frequency / sum(Frequency)) * 100, 1),
    `Cumulative %`   = round(cumsum(Percentage), 1)
  ) %>%
  arrange(desc(Frequency))

handedness_freq
```

**Finding:** Approximately `r round((sum(demo_complete$Handedness == "Right handed", na.rm=TRUE) / nrow(demo_complete)) * 100, 1)`% of participants are right-handed, consistent with general population estimates (85-90%).

#### Handedness by Condition

```{r handedness-condition-detailed}
handedness_cond <- demo_complete %>%
  group_by(Condition, Handedness) %>%
  summarise(Count = n(), .groups = "drop") %>%
  group_by(Condition) %>%
  mutate(
    Total             = sum(Count),
    `Percentage`      = round((Count / Total) * 100, 1)
  ) %>%
  ungroup()

handedness_cond %>%
  select(Condition, Handedness, Count, Percentage) %>%
  arrange(Condition, desc(Count))
```

#### Vision Frequency Distribution

```{r vision-frequency-detailed}
vision_freq <- demo_complete %>%
  count(Vision, name = "Frequency") %>%
  mutate(
    Percentage       = round((Frequency / sum(Frequency)) * 100, 1),
    `Cumulative %`   = round(cumsum(Percentage), 1)
  ) %>%
  arrange(desc(Frequency))

vision_freq
```

**Summary:** Most participants have normal or corrected-to-normal vision (`r round(sum(demo_complete$Vision %in% c("Normal", "Corrected to normal")) / nrow(demo_complete) * 100, 1)`%), ensuring visual stimuli were adequately perceived.

#### Vision by Condition

```{r vision-condition-detailed}
vision_cond <- demo_complete %>%
  group_by(Condition, Vision) %>%
  summarise(Count = n(), .groups = "drop") %>%
  group_by(Condition) %>%
  mutate(
    Total             = sum(Count),
    `Percentage`      = round((Count / Total) * 100, 1)
  ) %>%
  ungroup()

vision_cond %>%
  select(Condition, Vision, Count, Percentage) %>%
  arrange(Condition, desc(Count))
```

---

### Summary Tables

The table below summarises the full sample. *Characteristic* = the demographic variable or category being described; *Value* = the corresponding count or statistic.

```{r demo-summary-table}
tibble(
  `Demographic Characteristic` = c(
    "N — Number of participants with complete records",
    "Age — Mean (Standard Deviation)",
    "Age — Range (minimum to maximum)",
    "Gender — Female",
    "Gender — Male",
    "Handedness — Right-handed",
    "Handedness — Left-handed",
    "Vision — Normal (unaided)",
    "Vision — Corrected to normal (glasses or contact lenses)",
    "Vision — Uncorrected vision difficulty"
  ),
  `Value` = c(
    as.character(nrow(demo_complete)),
    sprintf("%.1f (%.1f)", mean(demo_complete$Age), sd(demo_complete$Age)),
    sprintf("%d – %d years", min(demo_complete$Age), max(demo_complete$Age)),
    as.character(sum(demo_complete$Gender == "Female", na.rm = TRUE)),
    as.character(sum(demo_complete$Gender == "Male",   na.rm = TRUE)),
    as.character(sum(demo_complete$Handedness == "Right handed", na.rm = TRUE)),
    as.character(sum(demo_complete$Handedness == "Left Handed",  na.rm = TRUE)),
    as.character(sum(demo_complete$Vision == "Normal",                        na.rm = TRUE)),
    as.character(sum(demo_complete$Vision == "Corrected to normal",           na.rm = TRUE)),
    as.character(sum(demo_complete$Vision == "Uncorrected vision difficulty", na.rm = TRUE))
  )
)
```

The table below breaks down demographics by experimental condition. **NB** = Natural Boundary condition; **AB** = Abrupt Boundary condition. *Age Mean* and *Age Std Dev* are in years.

```{r demo-by-condition-table}
demo_complete %>%
  group_by(Condition) %>%
  summarise(
    `Number of Participants` = n(),
    `Age Mean (years)`       = round(mean(Age), 1),
    `Age Std Dev (years)`    = round(sd(Age), 1),
    `Number Female`          = sum(Gender == "Female", na.rm = TRUE),
    `Number Male`            = sum(Gender == "Male",   na.rm = TRUE),
    `Right-handed`           = sum(Handedness == "Right handed", na.rm = TRUE),
    `Left-handed`            = sum(Handedness == "Left Handed",  na.rm = TRUE),
    .groups = "drop"
  )
```

## Participant-Level Aggregation

For statistical testing, **trial-level data** must be aggregated to the **participant level**. This is necessary because:

1. **Independence assumption**: Statistical tests (t-tests) assume each data point is independent. Multiple trials from the same participant are not independent.
2. **Unit of analysis**: Our experimental unit is the *participant*, not individual trials. We randomly assigned participants (not trials) to conditions.
3. **Avoid pseudoreplication**: Using all trials would artificially inflate sample size and violate statistical assumptions.

### Aggregation Strategy

Three aggregated datasets were created:

```{r aggregate-participants}
participant_level <- trial_df %>%
  group_by(participant_id, Condition) %>%
  summarise(mean_accuracy = mean(Accuracy, na.rm = TRUE),
            mean_rt       = mean(RT,       na.rm = TRUE),
            .groups = "drop")

cat("Participant-level dataset created:\n")
cat("  - Number of participants:", nrow(participant_level), "\n")
cat("  - NB condition:", sum(participant_level$Condition == "NB"), "participants\n")
cat("  - AB condition:", sum(participant_level$Condition == "AB"), "participants\n")
cat("  - Variables: participant_id, Condition, mean_accuracy, mean_rt\n")
```

```{r aggregate-participant-frametype}
participant_frametype <- trial_df %>%
  group_by(participant_id, Condition, FrameType) %>%
  summarise(mean_accuracy = mean(Accuracy, na.rm = TRUE), .groups = "drop")

cat("\nParticipant × FrameType dataset created:\n")
cat("  - Total rows:", nrow(participant_frametype), "\n")
cat("  - Variables: participant_id, Condition, FrameType, mean_accuracy\n")
cat("  - Used for: BB vs EM frame type analyses\n")
```

```{r demo-merge}
participant_demo <- participant_level %>%
  left_join(
    demo_complete %>% select(participant_id, Age, Gender, Handedness, Vision),
    by = "participant_id"
  ) %>%
  filter(!is.na(Age))

cat("\nMerged demographic + performance dataset created:\n")
cat("  - Participants with complete data:", nrow(participant_demo), "\n")
cat("  - Variables: participant_id, Condition, mean_accuracy, mean_rt, Age, Gender, Handedness, Vision\n")
cat("  - Used for: Demographic moderator analyses (Tests D3 & D4)\n")
```

**Result:** Each participant contributes exactly **one data point** to each statistical test, satisfying the independence assumption.

## Bonferroni Correction

### Why Multiple Comparison Correction is Necessary

When conducting **multiple statistical tests** on the same dataset, the probability of making at least one **Type I error** (false positive) increases with each additional test. This is known as the **multiple comparisons problem** or **family-wise error rate (FWER) inflation**.

**Example:** If we set α = 0.05 for each test:
- Probability of NOT making a Type I error on one test = 0.95
- Probability of NOT making a Type I error on 4 independent tests = 0.95^4^ = 0.814
- **Probability of making AT LEAST ONE Type I error = 1 - 0.814 = 0.186 (18.6%)**

This means that with 4 tests, we have nearly a 1 in 5 chance of incorrectly rejecting at least one true null hypothesis!

### Bonferroni Correction Solution

```{r bonferroni}
n_tests        <- 4
alpha_raw      <- 0.05
alpha_adjusted <- alpha_raw / n_tests

cat("Multiple comparison correction:\n")
cat("  - Number of primary hypothesis tests:", n_tests, "\n")
cat("  - Uncorrected alpha level:", alpha_raw, "\n")
cat("  - Bonferroni-adjusted alpha:", alpha_adjusted, "\n")
cat("  - Interpretation: p-values must be <", alpha_adjusted, "to be significant\n")
```

### Mathematical Formula

$$\alpha_{adjusted} = \frac{\alpha_{family-wise}}{k} = \frac{0.05}{4} = 0.0125$$

Where:
- $\alpha_{adjusted}$ = adjusted significance threshold for each individual test
- $\alpha_{family-wise}$ = desired family-wise error rate (conventionally 0.05)
- $k$ = number of tests in the family (4 primary hypothesis tests)

### Why Bonferroni for This Study?

1. **Conservative but appropriate**: Protects against false discoveries when testing related hypotheses
2. **Simple and transparent**: Easy to implement and report
3. **Controls FWER**: Maintains overall Type I error rate at 5% across all 4 tests
4. **Standard in psychology**: Widely accepted method for planned comparisons

### Which Tests Use Bonferroni?

**Primary hypothesis tests** (Bonferroni-adjusted α = 0.0125):
- Test 1: Overall accuracy (NB vs AB)
- Test 2: Overall RT (NB vs AB)
- Test 3: BB frame accuracy (NB vs AB)
- Test 4: EM frame accuracy (NB vs AB)

**Demographic tests** (unadjusted α = 0.05):
- Tests D1-D4 use α = 0.05 because they are exploratory checks, not primary hypotheses
- These assess randomization success and potential moderators
- Not part of the "family" of confirmatory tests

**Trade-off:** Bonferroni correction reduces statistical power (increases Type II error risk), but this is acceptable to maintain confidence in positive findings.

## Descriptive Statistics

### Overall Accuracy by Condition

Each row is one experimental condition. Values are computed at the **participant level** (each participant contributes one mean accuracy score averaged across all their trials). **NB** = Natural Boundary; **AB** = Abrupt Boundary. Accuracy is expressed as a proportion (0 = all wrong, 1 = all correct).

```{r desc-condition}
participant_level %>%
  group_by(Condition) %>%
  summarise(
    `Number of Participants`  = n(),
    `Mean Accuracy`           = round(mean(mean_accuracy), 3),
    `Standard Deviation`      = round(sd(mean_accuracy), 3),
    `Standard Error`          = round(sd(mean_accuracy) / sqrt(n()), 3),
    `Minimum Accuracy`        = round(min(mean_accuracy), 3),
    `Maximum Accuracy`        = round(max(mean_accuracy), 3),
    .groups = "drop"
  )
```

### Accuracy by Condition and Frame Type

Each row represents one Condition × Frame Type combination. **BB** = Before-Boundary frame (a frame adjacent to the event boundary); **EM** = Event-Middle frame (a frame from the middle of the event, away from the boundary). Accuracy is a proportion (0–1).

```{r desc-condition-frametype}
participant_frametype %>%
  group_by(Condition, `Frame Type` = FrameType) %>%
  summarise(
    `Number of Participants` = n(),
    `Mean Accuracy`          = round(mean(mean_accuracy), 3),
    `Standard Deviation`     = round(sd(mean_accuracy), 3),
    `Standard Error`         = round(sd(mean_accuracy) / sqrt(n()), 3),
    .groups = "drop"
  )
```

### Reaction Time and Confidence by Condition

Computed at the **trial level** (all retained trials pooled within each condition). *Response Time* is in seconds from image onset to key press. *Confidence Rating* is a 1–5 scale recorded immediately after each recognition response (1 = not at all confident, 5 = completely confident).

```{r desc-rt-conf}
trial_df %>%
  group_by(Condition) %>%
  summarise(
    `Number of Trials`            = n(),
    `Mean Response Time (s)`      = round(mean(RT, na.rm = TRUE), 3),
    `Std Dev Response Time (s)`   = round(sd(RT,   na.rm = TRUE), 3),
    `Mean Confidence Rating`      = round(mean(Confidence, na.rm = TRUE), 3),
    `Std Dev Confidence Rating`   = round(sd(Confidence,   na.rm = TRUE), 3),
    .groups = "drop"
  )
```

---

# Exploratory Data Analysis (EDA)

```{r shared-theme, include=FALSE}
brsm_theme <- theme_classic() +
  theme(
    plot.title    = element_text(face = "bold", size = 13),
    plot.subtitle = element_text(size = 10, colour = "grey40"),
    axis.title    = element_text(size = 11),
    axis.text     = element_text(size = 10),
    legend.title  = element_text(size = 10, face = "bold"),
    legend.text   = element_text(size = 9),
    strip.text    = element_text(face = "bold", size = 10)
  )

condition_colours <- c("NB" = "#2196F3", "AB" = "#F44336")
frametype_colours <- c("BB" = "#4CAF50", "EM" = "#FF9800")
```

---

### EDA 1 - Distribution of the Data

#### Figure 1A - Histogram of Accuracy

```{r fig1a-histogram, fig.keep='all'}
p1a <- ggplot(participant_level, aes(x = mean_accuracy, fill = Condition)) +
  geom_histogram(binwidth = 0.05, colour = "white", boundary = 0) +
  facet_wrap(~Condition, ncol = 1, labeller = label_both) +
  scale_fill_manual(values = condition_colours) +
  scale_x_continuous(limits = c(0.4, 1.05), breaks = seq(0.4, 1.0, 0.1),
                     labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure 1A. Histogram of Mean Recognition Accuracy per Participant",
       subtitle = "One value per participant (mean proportion correct across ~40 trials)",
       x = "Mean Accuracy (proportion correct)", y = "Number of Participants") +
  brsm_theme + theme(legend.position = "none")
print(p1a)
```

**Interpretation:** Both distributions are negatively skewed; most participants performed well above chance. NB distribution is shifted toward higher accuracy compared to AB.

#### Figure 1B - Density Plot of Accuracy

```{r fig1b-density, fig.keep='all'}
p1b <- ggplot(participant_level, aes(x = mean_accuracy, fill = Condition, colour = Condition)) +
  geom_density(alpha = 0.35, linewidth = 1.1) +
  scale_fill_manual(values = condition_colours) +
  scale_colour_manual(values = condition_colours) +
  scale_x_continuous(limits = c(0.4, 1.05), breaks = seq(0.4, 1.0, 0.1),
                     labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure 1B. Density Plot of Mean Recognition Accuracy by Condition",
       subtitle = "Smooth probability distribution; NB (blue) vs AB (red)",
       x = "Mean Accuracy (proportion correct)", y = "Density",
       fill = "Condition", colour = "Condition") +
  brsm_theme
print(p1b)
```

**Interpretation:** NB curve peaks slightly to the right of AB, indicating NB participants are concentrated at higher accuracy values.

---

### EDA 2 - Differences Between Conditions

#### Figure 2 - Violin Plot by Condition

```{r fig2a-violin-condition, fig.keep='all'}
p2a <- ggplot(participant_level, aes(x = Condition, y = mean_accuracy, fill = Condition)) +
  geom_violin(alpha = 0.5, trim = FALSE, linewidth = 0.8) +
  geom_boxplot(width = 0.12, outlier.shape = NA, alpha = 0.85, linewidth = 0.7) +
  geom_jitter(aes(colour = Condition), width = 0.08, alpha = 0.4, size = 1.8) +
  scale_fill_manual(values = condition_colours) +
  scale_colour_manual(values = condition_colours) +
  scale_y_continuous(limits = c(0.45, 1.05), breaks = seq(0.5, 1.0, 0.1),
                     labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure 2. Violin Plot of Accuracy by Condition",
       subtitle = "Shape = full distribution; inner box = median and IQR; dots = individual participants",
       x = "Condition", y = "Mean Accuracy") +
  brsm_theme + theme(legend.position = "none")
print(p2a)
```

**Interpretation:** NB violin is wider at higher accuracy values and sits at a higher median than AB.

---

### EDA 3 - Differences Between Frame Types

#### Figure 3A - Violin Plot by Frame Type

```{r fig3a-violin-frametype, fig.keep='all'}
p3a <- ggplot(participant_frametype, aes(x = FrameType, y = mean_accuracy, fill = FrameType)) +
  geom_violin(alpha = 0.5, trim = FALSE, linewidth = 0.8) +
  geom_boxplot(width = 0.12, outlier.shape = NA, alpha = 0.85, linewidth = 0.7) +
  geom_jitter(aes(colour = FrameType), width = 0.08, alpha = 0.4, size = 1.8) +
  scale_fill_manual(values = frametype_colours) +
  scale_colour_manual(values = frametype_colours) +
  scale_y_continuous(limits = c(0.45, 1.05), breaks = seq(0.5, 1.0, 0.1),
                     labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure 3A. Violin Plot of Accuracy by Frame Type",
       subtitle = "BB = Before Boundary; EM = Event Middle",
       x = "Frame Type", y = "Mean Accuracy") +
  brsm_theme + theme(legend.position = "none")
print(p3a)
```

**Interpretation:** BB violin sits at a higher median than EM, consistent with the Boundary Advantage Effect.

#### Figure 3B - Heatmap of Mean Accuracy by Condition x Frame Type

```{r fig3b-heatmap-frametype, fig.keep='all'}
interaction_means <- participant_frametype %>%
  group_by(Condition, FrameType) %>%
  summarise(N = n(), Mean = mean(mean_accuracy, na.rm = TRUE),
            SD = sd(mean_accuracy, na.rm = TRUE), SE = SD / sqrt(N),
            CI_low  = Mean - qt(0.975, df = N - 1) * SE,
            CI_high = Mean + qt(0.975, df = N - 1) * SE, .groups = "drop")

p3b <- ggplot(interaction_means, aes(x = FrameType, y = Condition, fill = Mean)) +
  geom_tile(colour = "white", linewidth = 1.5) +
  geom_text(aes(label = scales::percent(round(Mean, 3), accuracy = 0.1)),
            size = 6, fontface = "bold", colour = "white") +
  scale_fill_gradient(low = "#EF9A9A", high = "#1565C0", limits = c(0.80, 0.92),
                      labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure 3B. Heatmap of Mean Accuracy by Condition x Frame Type",
       subtitle = "Darker blue = higher accuracy",
       x = "Frame Type", y = "Condition", fill = "Mean Accuracy") +
  brsm_theme
print(p3b)
```

**Interpretation:** All four cells follow the same direction: NB > AB within each frame type, and BB > EM within each condition.

---

### EDA 4 - Group Means with Uncertainty (95% CI)

#### Figure 4 - Bar Chart with 95% CI

```{r fig4-ci-bar, fig.keep='all'}
p4 <- ggplot(interaction_means, aes(x = FrameType, y = Mean, fill = Condition)) +
  geom_col(position = position_dodge(width = 0.6), width = 0.55, alpha = 0.9) +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high),
                position = position_dodge(width = 0.6), width = 0.18, linewidth = 0.8) +
  scale_fill_manual(values = condition_colours) +
  scale_y_continuous(limits = c(0, 1.02), breaks = seq(0, 1, 0.2),
                     labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure 4. Mean Accuracy (+/- 95% CI) by Condition and Frame Type",
       subtitle = "Error bars = 95% Confidence Interval (t-distribution, df = n - 1)",
       x = "Frame Type", y = "Mean Accuracy", fill = "Condition") +
  brsm_theme
print(p4)
```

**Interpretation:** NB bars are taller than AB bars within both frame types. Confidence intervals are narrow and non-overlapping between NB and AB.

---

### EDA 5 - Participant Demographics

#### Figure 5A - Age Distribution by Condition

```{r fig5a-age-histogram, fig.keep='all'}
p5a <- ggplot(demo_complete, aes(x = Age, fill = Condition)) +
  geom_histogram(binwidth = 1, position = "dodge", alpha = 0.7, colour = "white") +
  scale_fill_manual(values = condition_colours) +
  scale_x_continuous(breaks = seq(18, 36, 2)) +
  labs(title = "Figure 5A. Age Distribution by Condition",
       subtitle = "Each bar = number of participants of that age",
       x = "Age (years)", y = "Number of Participants", fill = "Condition") +
  brsm_theme
print(p5a)
```

**Interpretation:** Both conditions share a similar age distribution (19-26 years). No visible age imbalance.

#### Figure 5B - Age Boxplot: NB vs AB

```{r fig5b-age-boxplot, fig.keep='all'}
p5b <- ggplot(demo_complete, aes(x = Condition, y = Age, fill = Condition)) +
  geom_boxplot(width = 0.45, outlier.shape = NA, alpha = 0.7, linewidth = 0.8) +
  geom_jitter(aes(colour = Condition), width = 0.12, alpha = 0.45, size = 1.8) +
  scale_fill_manual(values = condition_colours) +
  scale_colour_manual(values = condition_colours) +
  scale_y_continuous(breaks = seq(18, 36, 2)) +
  labs(title = "Figure 5B. Age by Condition (Boxplot)",
       subtitle = "Median, IQR, and individual participants",
       x = "Condition", y = "Age (years)") +
  brsm_theme + theme(legend.position = "none")
print(p5b)
```

**Interpretation:** Median age is virtually identical across NB and AB (both approximately 22 years).

#### Figure 5C - Gender Breakdown (Overall)

```{r fig5c-gender-bar, fig.keep='all'}
gender_counts <- demo_complete %>% count(Gender) %>% mutate(pct = n / sum(n))

p5c <- ggplot(gender_counts, aes(x = reorder(Gender, -n), y = n, fill = Gender)) +
  geom_col(width = 0.55, alpha = 0.85) +
  geom_text(aes(label = sprintf("%d\n(%.0f%%)", n, pct * 100)), vjust = -0.4, size = 4.2, fontface = "bold") +
  scale_fill_manual(values = c("Female" = "#E91E63", "Male" = "#1565C0")) +
  scale_y_continuous(limits = c(0, max(gender_counts$n) * 1.2)) +
  labs(title = "Figure 5C. Gender Breakdown of Participants",
       subtitle = "Full sample (complete demographic records only)",
       x = "Gender", y = "Number of Participants") +
  brsm_theme + theme(legend.position = "none")
print(p5c)
```

**Interpretation:** Sample is predominantly male (113 vs 50 female). Typical of convenience samples from certain university departments.

#### Figure 5D - Gender by Condition (Stacked Bar)

```{r fig5d-gender-condition, fig.keep='all'}
gender_cond <- demo_complete %>%
  count(Condition, Gender) %>%
  group_by(Condition) %>% mutate(pct = n / sum(n)) %>% ungroup()

p5d <- ggplot(gender_cond, aes(x = Condition, y = pct, fill = Gender)) +
  geom_col(position = "stack", width = 0.55, alpha = 0.85) +
  geom_text(aes(label = sprintf("%d\n(%.0f%%)", n, pct * 100)),
            position = position_stack(vjust = 0.5), size = 3.8, fontface = "bold", colour = "white") +
  scale_fill_manual(values = c("Female" = "#E91E63", "Male" = "#1565C0")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure 5D. Gender Composition by Condition",
       subtitle = "Proportional stacked bar; numbers = count and percentage within condition",
       x = "Condition", y = "Proportion of Participants", fill = "Gender") +
  brsm_theme
print(p5d)
```

**Interpretation:** Gender ratio is similar across both conditions (NB ~29% female; AB ~33% female).

#### Figure 5E - Handedness Distribution

```{r fig5e-handedness, fig.keep='all'}
handedness_counts <- demo_complete %>% 
  count(Handedness) %>% 
  mutate(pct = n / sum(n))

p5e <- ggplot(handedness_counts, aes(x = reorder(Handedness, -n), y = n, fill = Handedness)) +
  geom_col(width = 0.55, alpha = 0.85) +
  geom_text(aes(label = sprintf("%d\n(%.1f%%)", n, pct * 100)), 
            vjust = -0.4, size = 4.2, fontface = "bold") +
  scale_fill_manual(values = c("Right handed" = "#4CAF50", "Left Handed" = "#FF9800")) +
  scale_y_continuous(limits = c(0, max(handedness_counts$n) * 1.2)) +
  labs(title = "Figure 5E. Handedness Distribution",
       subtitle = "Proportion of right-handed vs left-handed participants",
       x = "Handedness", y = "Number of Participants") +
  brsm_theme + theme(legend.position = "none")
print(p5e)
```

**Interpretation:** Right-handed dominance (~90%) matches general population norms.

#### Figure 5F - Vision Status Distribution

```{r fig5f-vision, fig.keep='all'}
vision_counts <- demo_complete %>% 
  count(Vision) %>% 
  mutate(pct = n / sum(n))

p5f <- ggplot(vision_counts, aes(x = reorder(Vision, -n), y = n, fill = Vision)) +
  geom_col(width = 0.65, alpha = 0.85) +
  geom_text(aes(label = sprintf("%d\n(%.1f%%)", n, pct * 100)), 
            vjust = -0.4, size = 4, fontface = "bold") +
  scale_fill_manual(values = c("Normal" = "#2196F3", 
                                "Corrected to normal" = "#4CAF50",
                                "Uncorrected vision difficulty" = "#F44336")) +
  scale_y_continuous(limits = c(0, max(vision_counts$n) * 1.2)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15)) +
  labs(title = "Figure 5F. Vision Status Distribution",
       subtitle = "Visual acuity categories across all participants",
       x = "Vision Status", y = "Number of Participants") +
  brsm_theme + theme(legend.position = "none")
print(p5f)
```

**Interpretation:** Most participants can adequately perceive visual stimuli. The small proportion with uncorrected vision difficulty is balanced across conditions.

#### Figure 5G - Age Distribution (Histogram + Density)

```{r fig5g-age-density-hist, fig.keep='all'}
p5g <- ggplot(demo_complete, aes(x = Age)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 1, 
                 fill = "#2196F3", alpha = 0.6, colour = "white") +
  geom_density(linewidth = 1.2, colour = "#F44336") +
  geom_vline(aes(xintercept = mean(Age)), colour = "#FF9800", 
             linetype = "dashed", linewidth = 1, alpha = 0.7) +
  geom_vline(aes(xintercept = median(Age)), colour = "#4CAF50", 
             linetype = "dotted", linewidth = 1, alpha = 0.7) +
  annotate("text", x = mean(demo_complete$Age) + 1.5, y = 0.15, 
           label = sprintf("Mean = %.1f", mean(demo_complete$Age)), 
           colour = "#FF9800", fontface = "bold", size = 3.5) +
  annotate("text", x = median(demo_complete$Age) - 1.5, y = 0.13, 
           label = sprintf("Median = %.0f", median(demo_complete$Age)), 
           colour = "#4CAF50", fontface = "bold", size = 3.5) +
  scale_x_continuous(breaks = seq(18, 36, 2)) +
  labs(title = "Figure 5G. Age Distribution with Density Curve",
       subtitle = "Histogram overlaid with smooth density (red); dashed = mean, dotted = median",
       x = "Age (years)", y = "Density") +
  brsm_theme
print(p5g)
```

**Interpretation:** Age distribution is slightly right-skewed with concentration around 20-23 years. Mean and median are very close, suggesting near-normal distribution.

#### Figure 5H - Demographic Summary Heatmap

```{r fig5h-demo-heatmap, fig.keep='all', fig.width=10, fig.height=6}
# Create a summary matrix for heatmap
demo_matrix <- demo_complete %>%
  group_by(Condition, Gender, Handedness) %>%
  summarise(Count = n(), .groups = "drop")

p5h <- ggplot(demo_matrix, aes(x = paste(Gender, Handedness, sep = "\n"), 
                                y = Condition, fill = Count)) +
  geom_tile(colour = "white", linewidth = 1.5) +
  geom_text(aes(label = Count), size = 6, fontface = "bold", colour = "white") +
  scale_fill_gradient(low = "#BBDEFB", high = "#0D47A1") +
  labs(title = "Figure 5H. Demographic Composition Heatmap",
       subtitle = "Participant count by Condition × Gender × Handedness",
       x = "Gender and Handedness", y = "Condition", fill = "Count") +
  brsm_theme +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))
print(p5h)
```

**Interpretation:** All demographic subgroups are represented in both conditions, with male right-handed participants being the most common category.

---

# Statistical Tests

## Hypothesis Tests

**Reminder:** All four hypothesis tests use **Bonferroni-adjusted α = 0.0125** to control for multiple comparisons. A p-value must be less than 0.0125 (not 0.05) to be considered statistically significant.

```{r effect-sizes, include=FALSE}
cohens_d_indep <- function(x, y) {
  n1 <- length(x); n2 <- length(y)
  pooled_sd <- sqrt(((n1 - 1) * var(x) + (n2 - 1) * var(y)) / (n1 + n2 - 2))
  (mean(x) - mean(y)) / pooled_sd
}
label_d <- function(d) {
  ifelse(abs(d) >= 0.8, "large", ifelse(abs(d) >= 0.5, "medium",
    ifelse(abs(d) >= 0.2, "small", "negligible")))
}
```

### Test 1 - Overall Recognition Accuracy: NB vs AB (H1)

```{r ttest-accuracy-condition}
acc_NB <- participant_level %>% filter(Condition == "NB") %>% pull(mean_accuracy)
acc_AB <- participant_level %>% filter(Condition == "AB") %>% pull(mean_accuracy)
t1 <- t.test(acc_NB, acc_AB, var.equal = FALSE)
t1
```

### Test 2 - Overall Response Time: NB vs AB (H1)

```{r ttest-rt-condition}
rt_NB <- participant_level %>% filter(Condition == "NB") %>% pull(mean_rt)
rt_AB <- participant_level %>% filter(Condition == "AB") %>% pull(mean_rt)
t2 <- t.test(rt_NB, rt_AB, var.equal = FALSE)
t2
```

### Test 3 - Boundary Frame Accuracy: NB-BB vs AB-BB (H2)

```{r ttest-bb-condition}
bb_NB <- participant_frametype %>% filter(Condition == "NB", FrameType == "BB") %>% pull(mean_accuracy)
bb_AB <- participant_frametype %>% filter(Condition == "AB", FrameType == "BB") %>% pull(mean_accuracy)
t3 <- t.test(bb_NB, bb_AB, var.equal = FALSE)
t3
```

### Test 4 - Event-Middle Frame Accuracy: NB-EM vs AB-EM (H3)

```{r ttest-em-condition}
em_NB <- participant_frametype %>% filter(Condition == "NB", FrameType == "EM") %>% pull(mean_accuracy)
em_AB <- participant_frametype %>% filter(Condition == "AB", FrameType == "EM") %>% pull(mean_accuracy)
t4 <- t.test(em_NB, em_AB, var.equal = FALSE)
t4
```

---

## Demographic Tests (D1-D4)

**Note:** Demographic tests use **unadjusted α = 0.05** because they are exploratory analyses checking randomization success and potential moderators, not confirmatory hypothesis tests. They are not part of the primary "family" of tests requiring Bonferroni correction.

### Test D1 - Age Balance: NB vs AB (Randomisation Check)

```{r demo-test-d1}
age_NB <- participant_demo %>% filter(Condition == "NB") %>% pull(Age)
age_AB <- participant_demo %>% filter(Condition == "AB") %>% pull(Age)
td1 <- t.test(age_NB, age_AB, var.equal = FALSE)
td1
```

**Interpretation:** A non-significant result (p > 0.05) confirms age was balanced across conditions.

### Test D2 - Gender Balance: NB vs AB (Randomisation Check)

```{r demo-test-d2}
gender_table <- table(participant_demo$Gender, participant_demo$Condition)
print(gender_table)
td2 <- chisq.test(gender_table)
td2
```

**Interpretation:** A non-significant chi-squared result confirms gender was distributed similarly across conditions.

### Test D3 - Age as a Moderator of Recognition Accuracy

```{r demo-test-d3}
td3 <- cor.test(participant_demo$Age, participant_demo$mean_accuracy, method = "pearson")
td3
```

```{r demo-test-d3-scatter, fig.keep='all'}
p_d3 <- ggplot(participant_demo, aes(x = Age, y = mean_accuracy, colour = Condition)) +
  geom_point(alpha = 0.55, size = 2.2) +
  geom_smooth(method = "lm", se = TRUE, aes(group = 1), colour = "grey30", linewidth = 0.9, linetype = "dashed") +
  scale_colour_manual(values = condition_colours) +
  scale_y_continuous(limits = c(0.45, 1.05), labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = seq(18, 36, 2)) +
  labs(title = "Figure D3. Age vs Recognition Accuracy",
       subtitle = "Each point = one participant; dashed line = overall linear trend",
       x = "Age (years)", y = "Mean Recognition Accuracy", colour = "Condition") +
  brsm_theme
print(p_d3)
```

**Interpretation:** In this narrow university-age sample (mean ~22 years), age is expected to be a negligible predictor of memory performance.

### Test D4 - Gender as a Moderator of Recognition Accuracy

```{r demo-test-d4}
acc_female <- participant_demo %>% filter(Gender == "Female") %>% pull(mean_accuracy)
acc_male   <- participant_demo %>% filter(Gender == "Male")   %>% pull(mean_accuracy)

cat("Female: n =", length(acc_female), "| M =", round(mean(acc_female), 3), "| SD =", round(sd(acc_female), 3), "\n")
cat("Male:   n =", length(acc_male),   "| M =", round(mean(acc_male),   3), "| SD =", round(sd(acc_male),   3), "\n")

td4 <- t.test(acc_female, acc_male, var.equal = FALSE)
td4
```

```{r demo-test-d4-violin, fig.keep='all'}
p_d4 <- ggplot(participant_demo %>% filter(Gender %in% c("Female", "Male")),
               aes(x = Gender, y = mean_accuracy, fill = Gender)) +
  geom_violin(alpha = 0.5, trim = FALSE, linewidth = 0.8) +
  geom_boxplot(width = 0.12, outlier.shape = NA, alpha = 0.85, linewidth = 0.7) +
  geom_jitter(aes(colour = Gender), width = 0.08, alpha = 0.4, size = 1.8) +
  scale_fill_manual(values   = c("Female" = "#E91E63", "Male" = "#1565C0")) +
  scale_colour_manual(values = c("Female" = "#E91E63", "Male" = "#1565C0")) +
  scale_y_continuous(limits = c(0.45, 1.05), labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Figure D4. Recognition Accuracy by Gender",
       subtitle = "Shape = full distribution; box = median and IQR",
       x = "Gender", y = "Mean Recognition Accuracy") +
  brsm_theme + theme(legend.position = "none")
print(p_d4)
```

**Interpretation:** A non-significant result confirms male and female participants performed equivalently.

### Demographic Tests Summary Table

The table below summarises all four demographic tests. *Test ID* = test identifier (D1–D4); *Description* = what was being tested; *Test Type* = the statistical method used; *Test Statistic* = the computed value with degrees of freedom; *p-Value* = two-tailed probability; *Significant at p < .05* = whether the result passed the unadjusted alpha threshold of 0.05.

```{r demo-tests-summary-table}
tibble(
  `Test ID`                   = c("D1", "D2", "D3", "D4"),
  `Description`               = c(
    "Age balance between NB and AB conditions",
    "Gender balance between NB and AB conditions",
    "Correlation between age and recognition accuracy",
    "Difference in accuracy between female and male participants"
  ),
  `Statistical Test Used`     = c("Welch t-test", "Chi-squared test", "Pearson correlation", "Welch t-test"),
  `Test Statistic (with df)`  = c(
    sprintf("t(%.1f) = %.3f", td1$parameter, td1$statistic),
    sprintf("χ²(%d) = %.3f",  as.integer(td2$parameter), td2$statistic),
    sprintf("r = %.3f",        td3$estimate),
    sprintf("t(%.1f) = %.3f", td4$parameter, td4$statistic)
  ),
  `p-Value`                   = round(c(td1$p.value, td2$p.value, td3$p.value, td4$p.value), 4),
  `Significant at p < .05`    = c(td1$p.value, td2$p.value, td3$p.value, td4$p.value) < 0.05
)
```

---

# Results Summary

## Summary Table of All Tests

**Important:** All four tests use **Bonferroni-adjusted significance threshold of \u03b1 = 0.0125** (not 0.05) to control for multiple comparisons. This prevents inflating the family-wise error rate when conducting 4 related tests.

The table below summarises the four primary hypothesis tests. *Dependent Variable* = what was measured; *Mean NB / Mean AB* = participant-level means for each condition; *t-Statistic* = Welch t-test value; *Degrees of Freedom* = Welch–Satterthwaite approximation; *p-Value* = two-tailed probability; *Significant* = whether p is below the Bonferroni-adjusted threshold of **0.0125** (not 0.05); *Cohen's d* = standardised effect size (positive = NB > AB).

```{r results-table}
tibble(
  `Hypothesis Test`             = c(
    "Test 1 — Overall recognition accuracy: NB vs AB",
    "Test 2 — Overall response time: NB vs AB",
    "Test 3 — Before-Boundary frame accuracy: NB vs AB",
    "Test 4 — Event-Middle frame accuracy: NB vs AB"
  ),
  `Dependent Variable`          = c(
    "Mean accuracy (proportion correct)",
    "Mean response time (seconds)",
    "Mean accuracy for BB frames only",
    "Mean accuracy for EM frames only"
  ),
  `Mean NB`                     = round(c(mean(acc_NB), mean(rt_NB, na.rm=TRUE), mean(bb_NB), mean(em_NB)), 3),
  `Mean AB`                     = round(c(mean(acc_AB), mean(rt_AB, na.rm=TRUE), mean(bb_AB), mean(em_AB)), 3),
  `t-Statistic`                 = round(c(t1$statistic, t2$statistic, t3$statistic, t4$statistic), 3),
  `Degrees of Freedom`          = round(c(t1$parameter, t2$parameter, t3$parameter, t4$parameter), 1),
  `p-Value`                     = round(c(t1$p.value,   t2$p.value,   t3$p.value,   t4$p.value),   4),
  `Significant (p < .0125)`     = c(t1$p.value, t2$p.value, t3$p.value, t4$p.value) < alpha_adjusted,
  `Cohen's d (effect size)`     = round(c(
    cohens_d_indep(acc_NB, acc_AB),
    cohens_d_indep(rt_NB[!is.na(rt_NB)], rt_AB[!is.na(rt_AB)]),
    cohens_d_indep(bb_NB, bb_AB),
    cohens_d_indep(em_NB, em_AB)
  ), 3)
)
```

## Interpretation of Statistical Results

```{r results-narrative, echo=FALSE, results='asis'}
t1_sig <- ifelse(t1$p.value < alpha_adjusted, "statistically significant", "not statistically significant")
t2_sig <- ifelse(t2$p.value < alpha_adjusted, "statistically significant", "not statistically significant")
t3_sig <- ifelse(t3$p.value < alpha_adjusted, "statistically significant", "not statistically significant")
t4_sig <- ifelse(t4$p.value < alpha_adjusted, "statistically significant", "not statistically significant")

d1 <- cohens_d_indep(acc_NB, acc_AB)
d2 <- cohens_d_indep(rt_NB[!is.na(rt_NB)], rt_AB[!is.na(rt_AB)])
d3 <- cohens_d_indep(bb_NB, bb_AB)
d4 <- cohens_d_indep(em_NB, em_AB)

cat(sprintf(
"**Test 1 - Overall Accuracy (H1):** NB participants (M = %.3f) showed %s higher recognition accuracy than AB participants (M = %.3f), t(%.1f) = %.3f, p = %.4f (Bonferroni alpha = 0.0125). Cohen's d = %.3f (%s effect). %s

**Test 2 - Overall RT (H1):** The RT difference between NB (M = %.3f s) and AB (M = %.3f s) was %s, t(%.1f) = %.3f, p = %.4f. Cohen's d = %.3f (%s effect). %s

**Test 3 - BB Accuracy (H2):** Restricting to BB frames, NB (M = %.3f) showed %s higher accuracy than AB (M = %.3f), t(%.1f) = %.3f, p = %.4f. Cohen's d = %.3f (%s effect). %s

**Test 4 - EM Accuracy (H3):** For EM frames, NB (M = %.3f) vs AB (M = %.3f) was %s, t(%.1f) = %.3f, p = %.4f. Cohen's d = %.3f (%s effect). %s",

  mean(acc_NB), t1_sig, mean(acc_AB), t1$parameter, t1$statistic, t1$p.value, d1, label_d(d1),
  ifelse(t1$p.value < alpha_adjusted, "This supports **H1**: intact boundaries facilitate memory encoding.",
    "This does not support H1 at the adjusted threshold."),

  mean(rt_NB, na.rm=TRUE), mean(rt_AB, na.rm=TRUE), t2_sig, t2$parameter, t2$statistic, t2$p.value, d2, label_d(d2),
  ifelse(t2$p.value < alpha_adjusted, "This provides secondary support for **H1**: NB participants responded more quickly.",
    "Response times did not differ significantly between conditions."),

  mean(bb_NB), t3_sig, mean(bb_AB), t3$parameter, t3$statistic, t3$p.value, d3, label_d(d3),
  ifelse(t3$p.value < alpha_adjusted, "This supports **H2**: boundary-adjacent frames benefit from intact boundary processing.",
    "The BB accuracy difference did not reach the adjusted threshold (partial support for H2)."),

  mean(em_NB), mean(em_AB), t4_sig, t4$parameter, t4$statistic, t4$p.value, d4, label_d(d4),
  ifelse(t4$p.value >= alpha_adjusted, "This supports **H3**: event-middle frames are not differentially affected by the boundary condition.",
    "Contrary to H3, EM frame accuracy also differed significantly between conditions.")
))
```

---

# Conclusion and Future Directions

## Summary of Findings

This study investigated whether disrupting a video before its natural event boundary impairs recognition memory (H1), whether boundary-adjacent frames are remembered better in the NB condition (H2), and whether event-middle frames are unaffected by the boundary manipulation (H3).

Four Welch t-tests tested these hypotheses at the participant level with Bonferroni-adjusted alpha = 0.0125. The four demographic tests (D1-D4) confirmed age- and gender-balanced groups and showed no demographic moderators of accuracy, supporting internal validity.

Together, the results speak to the predictions of Event Segmentation Theory (Zacks et al., 2007): event boundaries trigger memory consolidation, and disrupting them selectively impairs memory encoding.

## Limitations

- **Forced-choice recognition** paradigm may underestimate the true impact of boundary disruption compared to free recall.
- The t-tests treat BB and EM as separate subsets; a **mixed ANOVA** (Condition × FrameType) would directly test the interaction.
- **Bonferroni correction** is conservative; FDR correction could be applied as an alternative.
- **Demographic limitations**: 
  - Sample is predominantly male (69% male, 31% female), limiting generalisability to female populations
  - Narrow age range (19-28 years, mostly university students) limits generalisability across lifespan
  - Likely WEIRD sample (Western, Educated, Industrialized, Rich, Democratic)
  - Handedness and vision quality were not tested as potential moderators (only age and gender)
  - Sample size limits power for demographic subgroup analyses and interaction effects

## Future Directions

### Analyses Feasible with Existing Data

The following extensions can be completed using the current dataset without additional data collection:

#### 1. **Confidence Rating Analysis**
We already collected confidence ratings (1-5 scale) but haven't analyzed them. Can test:
- Do NB participants express higher confidence than AB participants?
- Is there a Condition × FrameType interaction on confidence?
- Simple Welch t-tests comparing mean confidence: NB vs AB

#### 2. **Response Time Enhancement**
We tested overall RT (Test 2) but can extend:
- RT by frame type: Are BB frames recognized faster than EM frames?
- RT × Accuracy interaction: Do correct responses have different RT patterns than incorrect ones?
- Violin plots showing RT distributions by condition and frame type

#### 3. **Mixed ANOVA for Condition × FrameType Interaction**
Currently we tested BB and EM separately (Tests 3 & 4). A proper mixed ANOVA would:
- Test the **interaction** directly: Does the condition effect differ for BB vs EM frames?
- More appropriate than separate t-tests for within-subjects factor (FrameType)
- Can be done in R with `aov()` or `ezANOVA()`

#### 4. **Simple Demographic Interactions**
Using existing demographic data, test whether treatment effect varies by:
- **Condition × Gender**: Does the NB advantage differ for males vs females?
  - Split sample into Male/Female, compute NB-AB difference for each
  - Independent t-test comparing the difference scores
  - Visualization: interaction plot
- **Condition × Age Group**: Split age into 2-3 groups (e.g., 18-21, 22-25, 26+)
  - Test if younger vs older participants show different boundary sensitivity

#### 5. **Effect Size Contextualization**
We report Cohen's *d* but haven't interpreted it relative to the literature:
- Compare our effect sizes to published event segmentation studies
- Brief literature search (~10 relevant papers)
- Add 2-3 sentences contextualizing whether our effects are typical/smaller/larger

#### 6. **Recognition Memory Index (REC)**
Currently using raw accuracy. REC corrects for guessing/response bias:
- Formula: REC = (Hits + Correct Rejections) / Total Trials - 0.5
- Or: Hit Rate - False Alarm Rate (if we have lure trials coded separately)
- Rerun primary analyses with REC instead of raw accuracy

#### 7. **Additional Visualizations**
- Raincloud plots (density + boxplot + individual points combined)
- Interaction plots showing Condition × FrameType 
- Confidence × Accuracy calibration scatter plots
- Cumulative distribution functions (CDF) for RT

#### 8. **Video Stimuli Analysis**
Using the video metadata files (duration, repeat status):
- Do repeated videos show better recognition? (is_repeat = 1)
- Does video duration correlate with recognition accuracy?
- Are certain videos consistently easier/harder across participants?
- Item-level difficulty analysis

---

# References

Swallow, K. M., Zacks, J. M., & Abrams, R. A. (2009). Event boundaries in perception affect memory encoding and updating. *Journal of Experimental Psychology: General*, *138*(2), 236-257. https://doi.org/10.1037/a0015631

Zacks, J. M., Speer, N. K., Swallow, K. M., Braver, T. S., & Reynolds, J. R. (2007). Event perception: A mind-brain perspective. *Psychological Bulletin*, *133*(2), 273-293. https://doi.org/10.1037/0033-2909.133.2.273

---

*Report generated with R `r getRversion()` on `r Sys.Date()`.*
